---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
library(readxl)
```

```{r}
comms <- read.csv("../data/input/AttributesByCommunity.csv") %>% 
  select(-X) %>% 
  select(-totalSettlements)

commAssignments <- read.csv("../data/input/Officer_Community_Assignments.csv") %>% 
  mutate(Community_ID=as.integer(Community_ID)) %>% 
  filter(!is.na(Community_ID))

complaints <- read.csv("../data/input/Complaint_Dataset.csv")
settlements <- read.csv("../data/input/Settlements.csv")
```

### First, add how many officers are currently active
```{r}
currentStatus <- commAssignments %>% group_by(Community_ID) %>% 
  summarize(currentlyActive = sum(current_status)) %>% 
  mutate(currentlyActive = ifelse(is.na(currentlyActive),0,currentlyActive))
comms <- comms %>% left_join(currentStatus, by = "Community_ID")
```



### Second add how many documents there are that list more than 1 officer in that community.
```{r}
#Need to add how many documents we have for each community
docs <- read_xls("../data/input/first 4 batches.xls")[1:2]
names(docs)[2] = "Num_of_Docs"
docs <- docs %>% group_by(CRID) %>% summarize(Num_of_Docs = sum(Num_of_Docs)) %>% arrange(CRID)


# for each community, pull CRIDS, then filter docs down to those CRIDS and add these up for those CRIDS.
numberOfDocs<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>% pull(CRID)
  val <- docs %>% filter(CRID %in% crids) %>% pull(Num_of_Docs) %>% sum()
  return(val)
}

comms <- comms %>% group_by(Community_ID) %>% mutate(NumberOfDocs2OrMoreListed = numberOfDocs(Community_ID)) %>% 
  mutate(AvgNumberOfDocs = NumberOfDocs2OrMoreListed/Count)
```


### Next get the number of document requests that people have requested on complaints involving more than 1 officer in that community.
```{r}
documentRequests <- read.csv("../data/input/Document requests from CPDP users.csv") %>%
  mutate(CRID = as.integer(gsub("C", "", allegation_id))) %>%
  count(CRID) %>%
  rename(Num_of_Doc_Requests = n)

numberOfDocRequests<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>% pull(CRID)
  val <- documentRequests %>% filter(CRID %in% crids) %>% pull(Num_of_Doc_Requests) %>% sum()
  return(val)
}
comms <- comms %>% ungroup() %>% group_by(Community_ID) %>% mutate(NumberOfDocRequests = numberOfDocRequests(Community_ID)) %>% ungroup()
```

### Add the pinboard URL 
```{r}
officerAssignments <- commAssignments %>%
  group_by(Community_ID) %>% 
  summarize(officers = paste(sort(unique(UID)),collapse=",")) %>% 
  mutate(link = paste0("http://beta.cpdp.co/pinboard/?officer-ids=",officers,"&title=C",Community_ID)) %>% 
  ungroup() %>% 
  select(-officers)
comms <- comms %>% left_join(officerAssignments, by = "Community_ID")
```

### Add total number of distinct settlements involving at least one officer in the community.
```{r}
numberOfSettlements<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  payouts <- settlements %>% filter(UID %in% uids) %>% distinct(case_id) %>%  pull(case_id)
  return(length(payouts))
}
valueOfSettlements <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  payouts <- settlements %>% filter(UID %in% uids) %>% distinct(case_id, .keep_all = TRUE) %>%  pull(settlement) %>% sum()
  return(payouts)
}

comms <- comms %>% group_by(Community_ID) %>% mutate(numberOfDistinctSettlements = numberOfSettlements(Community_ID), TotalPayouts = valueOfSettlements(Community_ID))
```




```{r}
NumberOfUseOfForce2OrMore <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "Use Of Force") %>% distinct(CRID)
  return(nrow(subset))
}
NumberOfIllegalSearch2OrMore<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "Illegal Search")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfFalseArrest2OrMore<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "False Arrest")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfOpsPersonnel2OrMore<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "Operation/Personnel Violations")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfCriminalMisconduct2OrMore<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "Criminal Misconduct")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfVerbalAbuse<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Category== "Verbal Abuse")%>% distinct(CRID)
  return(nrow(subset))
}


comms <- comms %>% group_by(Community_ID) %>% 
  mutate(
    UseOfForce_2orMore =NumberOfUseOfForce2OrMore(Community_ID),
    IllegalSearch_2orMore =NumberOfIllegalSearch2OrMore(Community_ID),
    FalseArrest_2orMore =NumberOfFalseArrest2OrMore(Community_ID),
    OpsPersonnel_2orMore =NumberOfOpsPersonnel2OrMore(Community_ID),
    CriminalMisconduct_2orMore =NumberOfCriminalMisconduct2OrMore(Community_ID),
    VerbalAbuse_2orMore =NumberOfVerbalAbuse(Community_ID)
  )
```


```{r}

NumberOfSustained<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Finding=="Sustained")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfNotSustained <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Finding=="Not Sustained	")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfNoAffidavit<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Finding=="No Affidavit")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfExonerated<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Finding=="Exonerated")%>% distinct(CRID)
  return(nrow(subset))
}

NumberOfUnfounded<- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(Finding=="Unfounded")%>% distinct(CRID)
  return(nrow(subset))
}

comms <- comms %>% group_by(Community_ID) %>% 
  mutate(
    NumberOfSustained_2orMore =NumberOfSustained(Community_ID),
    NumberOfNotSustained_2orMore =NumberOfNotSustained(Community_ID),
    NumberOfNoAffidavit_2orMore =NumberOfNoAffidavit(Community_ID),
    NumberOfExonerated_2orMore =NumberOfExonerated(Community_ID),
    NumberOfUnfounded_2orMore =NumberOfUnfounded(Community_ID)
  )
comms
```


### Add in outcomes
```{r}
outcomes <- complaints %>% mutate(outcome = ifelse(grepl("Suspen", Outcome), "Suspension", Outcome)) %>% mutate(outcome = ifelse(grepl("Reinstated", Outcome), "Reinstated", Outcome))

NoActionTaken <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="No Action Taken")%>% distinct(CRID)
  return(nrow(subset))
}

PenaltyNotServed <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Penalty Not Served")%>% distinct(CRID)
  return(nrow(subset))
}

Resigned <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Resigned")%>% distinct(CRID)
  return(nrow(subset))
}

Reprimand <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Reprimand")%>% distinct(CRID)
  return(nrow(subset))
}

AdministrativeTermination <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Administrative Termination")%>% distinct(CRID)
  return(nrow(subset))
}

Reinstated <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Reinstated")%>% distinct(CRID)
  return(nrow(subset))
}

Suspension <- function(comm){
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  subset <- outcomes %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% filter(outcome=="Suspended")%>% distinct(CRID)
  return(nrow(subset))
}

comms <- comms %>% group_by(Community_ID) %>% 
  mutate(
    noActionTaken_2orMore = NoActionTaken(Community_ID),
    PenaltyNotServed_2orMore = PenaltyNotServed(Community_ID),
    Resigned_2orMore = Resigned(Community_ID),
    Reprimand_2orMore = Reprimand(Community_ID),
    AdministrativeTermination_2orMore = AdministrativeTermination(Community_ID),
    Reinstated_2orMore = Reinstated(Community_ID),
    Suspension_2orMore = Suspension(Community_ID)
  )
```


### Add complainant information for each crew
```{r}
blackmales <- read_xlsx("../data/input/complainants/blackmales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "Black Male") %>% 
  distinct(CRID, Vic)

blackfemales <- read_xlsx("../data/input/complainants/blackfemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "Black Female") %>% 
  distinct(CRID, Vic)

whitemales <- read_xlsx("../data/input/complainants/whitemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "White Male") %>% 
  distinct(CRID, Vic)

whitefemales <- read_xlsx("../data/input/complainants/whitefemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "White Female") %>% 
  distinct(CRID, Vic)

hispanicmales <- read_xlsx("../data/input/complainants/hispanicmales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "Hispanic Male") %>% 
  distinct(CRID, Vic)

hispanicfemales <- read_xlsx("../data/input/complainants/hispanicfemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "Hispanic Female") %>% 
  distinct(CRID, Vic)

naanmales <- read_xlsx("../data/input/complainants/naanmales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "NAAN Male") %>% 
  distinct(CRID, Vic)

naanfemales <- read_xlsx("../data/input/complainants/naanfemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "NAAN Female") %>% 
  distinct(CRID, Vic)

apimales <- read_xlsx("../data/input/complainants/asianpacificislandermales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "API Male") %>% 
  distinct(CRID, Vic)

apifemales <- read_xlsx("../data/input/complainants/asianpacificislanderfemales.xlsx", sheet = "Allegations") %>% 
  mutate(Vic = "API Female") %>% 
  distinct(CRID, Vic)

allVics <- blackmales %>% 
  rbind(blackfemales) %>% 
  rbind(whitemales)%>% 
  rbind(whitefemales) %>% 
  rbind(hispanicmales)%>% 
  rbind(hispanicfemales) %>% 
  rbind(naanmales)%>% 
  rbind(naanfemales) %>% 
  rbind(apimales)%>% 
  rbind(apifemales) %>% 
  mutate(Victim=Vic) %>% 
  tidyr::separate(Vic, c("Race", "Gender"))

#allVics %>% write.csv("../data/output/Complainants.csv")
```

```{r}
allVics

blackComplainants <- function(community_ID){
  uids <- commAssignments %>% filter(Community_ID ==community_ID) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>%  pull(CRID)
  subset <- allVics  %>% filter(CRID%in% crids)%>% filter(Race=="Black")
  return(nrow(subset))
}

whiteComplainants <- function(community_ID){
  uids <- commAssignments %>% filter(Community_ID ==community_ID) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>%  pull(CRID)
  subset <- allVics  %>% filter(CRID%in% crids)%>% filter(Race=="White")
  return(nrow(subset))
}

hispanicComplainants <- function(community_ID){
  uids <- commAssignments %>% filter(Community_ID ==community_ID) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>%  pull(CRID)
  subset <- allVics  %>% filter(CRID%in% crids)%>% filter(Race=="Hispanic")
  return(nrow(subset))
}

maleComplainants <- function(community_ID){
  uids <- commAssignments %>% filter(Community_ID ==community_ID) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>%  pull(CRID)
  subset <- allVics  %>% filter(CRID%in% crids)%>% filter(Gender=="Male")
  return(nrow(subset))
}

femaleComplainants <- function(community_ID){
  uids <- commAssignments %>% filter(Community_ID ==community_ID) %>% pull(UID)
  crids <- complaints %>% filter(UID %in% uids) %>% group_by(CRID) %>% filter(n()>1) %>% ungroup() %>% distinct(CRID) %>%  pull(CRID)
  subset <- allVics  %>% filter(CRID%in% crids)%>% filter(Gender=="Female")
  return(nrow(subset))
}

comms <- comms %>% 
  group_by(Community_ID) %>% 
  mutate(
    blackComplainants_2orMore = blackComplainants(Community_ID),
    whiteComplainants_2orMore = whiteComplainants(Community_ID),
    hispanicComplainants_2orMore = hispanicComplainants(Community_ID),
    maleComplainants_2orMore = maleComplainants(Community_ID),
    femaleComplainants_2orMore = femaleComplainants(Community_ID)
  )

```
```{r}
comms
```
### ADD IN TRR DATA
```{r}
main <- read.csv("../data/input/TRR/TRR-main_2004-2016_2016-09.csv")

officers <- read.csv("../data/input/TRR/TRR-officers_2004-2016_2016-09.csv")%>%
  select(trr_id, injured, link_UID)%>% 
  rename(UID = link_UID)

subjectWeapons <- read.csv("../data/input/TRR/TRR-subject-weapons_2004-2016_2016-09.csv") %>% 
  mutate(vicWeapon = ifelse(weapon_type =="OTHER (SPECIFY)", weapon_description, weapon_type))%>%
  select(trr_id, vicWeapon)

officerWeapons <- read.csv("../data/input/TRR/TRR-weapon-discharges_2004-2016_2016-09.csv") %>% 
  mutate(officerWeapon = ifelse(weapon_type =="OTHER (SPECIFY)", weapon_type_description, weapon_type)) %>% 
  select(trr_id, officerWeapon)

subjects<- read.csv("../data/input/TRR/TRR-subjects_2004-2016_2016-09.csv") %>% 
  select(trr_id, gender, race, age, armed, injured) %>% 
  rename(vicGender = gender,
         vicRace= race,
         vicAge = age,
         vicArmed = armed,
         vicInjured = injured)
dischargeHits <- read.csv("../data/input/TRR/TRR-discharge-hits_2004-2016_2016-09.csv") %>% 
  select(trr_id, object_struck_of_discharge)

main <- main %>% 
  left_join(officers, by = "trr_id")  %>% 
  left_join(subjects, by = "trr_id") %>% 
  left_join(officerWeapons, by = "trr_id") %>% 
  left_join(subjectWeapons , by = "trr_id") %>% 
  left_join(dischargeHits , by = "trr_id")

other <- c("FIREARM - REVOLVER", "OFFICER DRAGGED BY VEHICLE", "SUBJECT POINTED WEAPON AT R/O", "VEHICLE - ATTEMPTED TO STRIKE OFFICER WITH VEHICLE", "VEHICLE - OFFICER STRUCK WITH VEHICLE", "VEHICLE")
shotUnarmedVic <- main %>% filter(vicArmed=="No") %>% filter(firearm_used==1) %>% filter(vicInjured=="Yes") %>% filter(!(vicWeapon %in% other)) %>% filter(object_struck_of_discharge %in% c("BOTH", "PERSON")) %>% pull(trr_id)
main <- main %>% mutate(shotUnarmedVic = ifelse(trr_id %in% shotUnarmedVic, "Yes", "No"))

commsTRR <- commAssignments %>% select(UID, Community_ID) %>% 
  left_join(main, by = "UID") %>% 
  group_by(Community_ID) %>% 
  summarize(totalTRRs = n(), 
            totalShotUnarmedVic = sum(shotUnarmedVic=="Yes"),
            totalTRRsWithFirearm = sum(firearm_used),
            totalTRRsWithTasers = sum(taser),
            totalIncidentsShotFirearmOrTaserFirst = sum(party_fired_first=="MEMBER"),
            totalBlackTRRVics = sum(vicRace=="BLACK"),
            totalWhiteTRRVics = sum(vicRace=="WHITE"),
            totalHispanicTRRVics = sum(vicRace=="HISPANIC"),
            totalMaleTRRVics = sum(vicGender =="MALE"), 
            totalFemaleTRRVics = sum(vicGender =="FEMALE"),
            averageTRRVicAge = mean(vicAge, na.rm=TRUE)
            )
commsTRR[is.na(commsTRR)] <- 0
comms <- comms %>% left_join(commsTRR, by = "Community_ID") %>% 
  mutate(
    AvgTRRsPerOfficer = totalTRRs/Count,
    AvgTRRsWithFirearmPerOfficer= totalTRRsWithFirearm/Count,
    AvgTRRsWithTaserPerOfficer= totalTRRsWithTasers/Count
  )
```

### Generate ordered list of which complaints to read.

```{r}
topics <- read.csv("../data/output/documentAssignments.csv") %>% 
  distinct(Topic_1, Topic_2, Topic_3, Topic_4, Topic_5, Topic_6, Topic_7, Topic_8, Topic_9, Topic_10, Topic_11,Topic_12, Topic_13, Topic_14, .keep_all = TRUE) %>% 
  filter(!is.na(text)) %>% 
  filter(column_name=="Initial / Intake Allegation") %>% 
  distinct(cr_id, .keep_all = TRUE) %>% 
  mutate(
    ImproperSearchOrDamage = ifelse(Topic_1>0.1, 1, 0),
    FalseArrestOrForce = ifelse(Topic_2>0.1, 1, 0),
    CellPhone = ifelse(Topic_3>0.1, 1, 0),
    ProfanityVerbalAbuse = ifelse(Topic_4>0.1 |Topic_6>0.1, 1, 0),
    PhysicalForce = ifelse(Topic_5>0.1, 1, 0),
    Inventory = ifelse(Topic_7>0.1, 1, 0),
    TrafficStop = ifelse(Topic_8>0.1 | Topic_9>0.1, 1, 0),
    RaceGenderClothes = ifelse(Topic_11>0.1, 1, 0),
    WeaponDetainmentOrDrugs = ifelse(Topic_13>0.1, 1, 0),
    Family = ifelse(Topic_14>0.1, 1, 0),
    FailureToDoSomething = ifelse(Topic_15>0.1, 1, 0)
  )
flagged <- topics %>% 
  select(cr_id, text) %>% 
  cbind(topics[,27:37]) %>%
  as.data.frame() %>% 
  rename(CRID = cr_id) %>% 
  left_join(complaints) %>% 
  filter(!is.na(Category))%>%
  mutate(Val = ImproperSearchOrDamage+ FalseArrestOrForce+ ProfanityVerbalAbuse+ PhysicalForce+ WeaponDetainmentOrDrugs) %>%
  arrange(-Val)

GetComplaints <- function(comm)
{
  uids <- commAssignments %>% filter(Community_ID ==comm) %>% pull(UID)
  crids <-complaints %>% filter(UID %in% uids) %>% pull(CRID)
  val <- flagged %>% filter(CRID %in% crids) %>% pull(CRID)
  val <- paste(val,collapse=", ")
  if(val==""){
    return("")
  }
  return(val)
}

comms <- comms %>% group_by(Community_ID) %>% mutate(ToRead_ordered = GetComplaints(Community_ID)) %>% ungroup()
```


### Export this dataset
```{r}
comms %>% write.csv("../data/output/BigCommunityDataset.csv")
```

```{r}
comps <- read.csv("/Volumes/N3_LAB/core_misconduct_data/from_invinst/fully-unified-data_08-28-18/complaints/complaints-accused.csv") %>% left_join(read.csv("/Volumes/N3_LAB/core_misconduct_data/from_invinst/fully-unified-data_08-28-18/complaints/complaints-complaints.csv"),by = "cr_id")
```
```{r}
comps %>% filter(!is.na(link_UID))%>% filter(!is.na(cr_id))
```
```{r}

```



